### 2020-04-03 draft.tex
fixed little bugs
more writing

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

\begin{lem}
The Yoneda embedding $\yo : \downarrow\op \to \Set^{\downarrow}$ is equal to the
composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Set
\xto{!_{(-)}} \Set^{\downarrow}.$$

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
TODO
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}
\dis{How does this topos compare to the topos $\Dir_{/D}$?}
\jaz{The following story: it generalizes to $\infty$-categories, which is why
  I'm writing it this way.}

\begin{defn}
A \emph{modality} on a category $\Ca$ is a stable orthogonal factorization
system $(\La, \Ra)$. \jaz{see Anel Biederman Finster Joyal \cite{ABFJ:Blakers.Massey}}

A modality is \emph{lex} if for any square
\[
  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAEEQBfU9TXfIRRkAjFVqMWbAELdeIDNjwEiI8uPrNWiEAGE5fJYNWkx1TVJ0ARbuJhQA5vCKgAZgCcIAWyRkQOCCQAJnNJbRBXAwjPH0QQ-0DEAGZQrTYHKI9vX2oApDUQBjoAIxgGAAV+ZSEQdywHAAscEFTLEAbMmPzcxJSJNJ0AaxbCkrLKoxUdOsbmrgouIA
\begin{tikzcd}
A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
B \arrow[r, "k"']                & D               
\end{tikzcd}
\]
where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)

\begin{prop}
If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
\Ra_X)$ on $\Ca_{/X}$ \jaz{I'll flesh this out in a bit, see
  \cite{ABFJ:Blakers.Massey}}. If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
\end{prop}

\begin{prop}
There is an equivalence between the order of lex modalities on a topos and the
order of subtoposes.
\end{prop}
\begin{proof}
Idea: we take those objects whose terminal morphism is in $\Ra$.
\end{proof}

\begin{prop}
The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
$\Set^{\downarrow}$ (given by the cartesian fibration $\Set\op \to \Set$) is a
lex modality.
\end{prop}

\begin{thm}
The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
$\Set^{\downarrow}_{/\pi}$ exhibits $\Set^{\downarrow}_{/_{\ulcorner} \pi}$ as a
subtopos.

As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
  $\Set^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
  D}$ as a sheaf topos?}
\end{thm}

@@

@@

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b : B} E_b^S,$$
    or equivalently the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item The restricted representable functor
  $\Ha^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \down \xto{\pi} \Ha)$$
  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Ha$ over $S$.
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Ha)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone}.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \down \xto{\pi} \Ha)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Noting that $\Hom_{\Ha}(!_0, S) = \Hom_{\Ha\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Ha}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}} \xto{!_0} \Ha$. Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
preserves weakly contractible colimits, {\color{red} TODO}.

Finally, we calculate $\Ha^{\down}(!_{\ast}, \pi)$ homotopy type-theoretically:
\begin{align*}
\Ha^{\down}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
                                  (\pi \circ f = b \circ !_X)\\
                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
                                  &\equiv \sum_{b : B}E_b^X.
\end{align*}
{\color{red} But I need a better argument to show that this is a natural
  equivalence of functors --- something involving cartesian fibrations etc etc etc}
\end{proof}

@@

Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
\xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
Lemma \ref{lem:extending.diagram.with.initial.object.has.same.colimit}). Therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

@@

As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.type.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.type.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.type.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
\[
\begin{tikzcd}[sep=small]
  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
  D(1)\ar[rr, crossing over]&&
  D'(1)\ar[dd]\\
  1\ar[dr]\ar[rr, equal]&&
  1\ar[dr]\ar[dl, dotted]\\&
  D(0)\ar[from=uu, crossing over]\ar[rr]&&
  D'(0)
\end{tikzcd}
\]
We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
saying that there are unique dotted arrows making the diagram commute. So, we
need to show that if the front face is a pullback, then there are unique
diagonal dotted arrows as shown in the homotopy type-theoretical sense.
{\color{red} TODO} 
\end{proof}

@@

@@

\section{Appendix}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}

\begin{lem}\label{lem:kan.extending.cone.adds.initial}
If $\Ca$ is an $\infty$-category with an initial object, then the restriction
$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
initial object. 
\end{lem}
\begin{proof}

\end{proof}

\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
\end{lem}
\begin{proof}
For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that 
\end{proof}

>>>>

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

\begin{lem}\label{lem:set.bundle.yoneda}
The Yoneda embedding $\yo : \downarrow\op \to \Set^{\downarrow}$ is equal to the
composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Set
\xto{!_{(-)}} \Set^{\downarrow}.$$

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
  \jaz{Need to find a good citation for this result --- that polynomial functors
  and cartesian transforms are bundles and cartesian maps (for 1-cats).}
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}
\dis{How does this topos compare to the topos $\Dir_{/D}$?}
\jaz{See the $\infty$-categorical case. The same story can be told for
  1-categories, but perhaps we should tell it some other way?}

@@

\begin{lem}\label{lem:type.bundle.yoneda}
The Yoneda embedding $\yo : \downarrow\op \to \Ha^{\downarrow}$ is equivalent to the
composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Ha
\xto{!_{(-)}} \Ha^{\downarrow}.$$

As a corollary, for any $\pi : \downarrow \to \Ha$, $\down\op \xto{\sigma\op}
\down \xto{\pi} \Ha$ equals the composite
$$\down\op \xto{!_0\op} \Ha\op \xto{!_{(-)}\op}
(\Ha^{\downarrow})\op \xto{\Ha^{\downarrow}(-, \pi)} \Ha$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
  This follows from Lemma \ref{lem:set.bundle.yoneda}, since $\downarrow$ is a $1$-category.
\end{proof}

@@

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b : B} E_b^S,$$
    or equivalently the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item The pullback functor sending a set $S$ to 
\[
\begin{tikzcd}
	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Ha(S,E)\ar[r]&
	\Ha(S,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Ha^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha)$$
  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Ha$ over $S$.
\item The functor
  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
  \xto{\pi} \Ha)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone}.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Ha)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Ha}(!_0 \circ \sigma\op,
S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
comma squares. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Ha}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Ha}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha).$$
This gives us the equivalence between (1) and (5). By Lemma
\ref{lem:slice.cone.equiv}, we see also that (5) and (6) are equivalent.

Now, using Lemmas \ref{lem:bang.preserves.weakly.contractible.colimits} and \ref{lem:type.bundle.yoneda}, we may make
the following calculation identifying (4) with (6):

\begin{align*}
  \Ha^{\down}(!_S, \pi) &= \Ha^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha)}, \pi) \\
  &\simeq \Ha^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha \xto{!_{(-)}} \Ha^{\down}), \pi)\\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Ha\op \xto{!_{(-)}} (\Ha^{\down})\op \xto{\Ha^{\down}(-, \pi)} \Ha) \\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Ha).
\end{align*}

\jaz{TODO: (3) with (4) and (2) and (4)}
\end{proof}

@@

Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Ha$ by Lemma \ref{lem:every.type.weakly.contractible.colimit}. Therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

@@

As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.type.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.type.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Ha$. We will freely use the natural isomorphism
$D(X)\cong\Ha^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.type.cart2} with
\begin{equation}\label{eqn.type.cart3}
\begin{tikzcd}
 \Ha^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Ha^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Ha^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Ha^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

For the if direction, note that Diagram \ref{eqn.type.cart3} is a pullback
whenever Diagram \ref{eqn.type.cart1} is, as vertical maps are orthogonal to
cartesian maps in $\Ha^{\down}$.
\end{proof}

@@

Now, since $\Dir$ is a topos, so is $\Dir_{/D}$. And, as we saw above,
$\Dir_{/_{\ulcorner} D}$ is a topos as well. What is the relationship between
$\Dir_{/D}$ and $\Dir_{/_{\ulcorner} D}$?

We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ induced
by a \emph{lex modality} on $\Dir_{/D}$. We will recall the definition of a lex
modality and its basic theory here, before applying it to prove our desired
theorem. Modalities were defined in Homotopy Type Theory in the HoTT Book
\cite{UFP:HoTT.Book}, and their theory developed substantially in
\cite{RSS:Modalities.in.HoTT}. This theory was externalized to
$\infty$-toposes in \cite{ABFJ:Blakers.Massey} and \cite{ABFJ:Goodwillie} as a
efficient way for working with localizations of $\infty$-toposes.

\begin{defn}
A \emph{modality} on an $\infty$-topos $\Ca$ is a stable orthogonal factorization
system $(\La, \Ra)$. This is an orthogonal factorization system in which the
left class is stable under pullback.

A modality is \emph{lex} if for any square
\[
\begin{tikzcd}
A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
B \arrow[r, "k"']                & D               
\end{tikzcd}
\]
where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)

\begin{prop}
If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
\Ra_X)$ on $\Ca_{/X}$ where $\La_X$ (resp. $\Ra$) consists of those maps in $\Ca_{/X}$
whose image under the forgetful functor to $\Ca$ is in $\La$ (resp. $\Ra$).

If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
\end{prop}
\begin{proof}
\jaz{That this forms an orthogonal factorization system is claimed without proof
as Lemma 3.1.7 in \cite{ABFJ:Blakers.Massey}. TODO would be to prove this
fully.}

Recall that the forgetful functor $\Ca_{/X} \to \Ca$ creates pullbacks. Therefore,
$(\La_X, \Ra_X)$ is a modality --- $\La_X$ is closed under pullback since $\La$
is. Furthermore, if $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$ because the
necessary diagram is a pullback if and only if its underlying diagram in $\Ca$
is one. 
\end{proof}

\begin{prop}
  For any lex modality $(\La, \Ra)$ on an $\infty$-topos $\Ca$, we get a subtopos
  consisting of those objects $X \in \Ca$ for which the terminal map $!_X : X
  \to \ast$ is in $\Ra$. This includes the order of lex modalities into the
  order of subcategories of $\Ca$ whose image consists of precisely the subtoposes.
\end{prop}
\begin{proof}
\jaz{TODO. I
  think I can find a citation for this --- it is certainly folklore. I'll check \cite{RSS:Modalities.in.HoTT}.}
\end{proof}

\begin{prop}
The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
$\Ha^{\downarrow}$ (given by the cartesian fibration $\Ha\op \to \Ha$) is a
lex modality.
\end{prop}
\begin{proof}
\jaz{TODO: Cite a proof that this is an orthogonal factorization system.}

  Vertical morphisms of bundles are closed under pullback since pullbacks are
computed pointwise and the pullback of an equivalence is an equivalence. The
modality is lex because in the following cube:
\[
    \begin{tikzcd}[row sep=1.5em, column sep = 1.5em]
    A_1 \arrow[rr] \arrow[dr, crossing over] \arrow[dd,swap] \arrow[ddrr, phantom, "\ulcorner"
    very near start] &&
    C_1 \arrow[dd] \arrow[dr] \\
    & B_1 \arrow[rr, crossing over]\arrow[dd, crossing over] \arrow[ddrr,
    phantom, "\ulcorner" very near start]&&
    D_1 \arrow[dd,"h"] \\
    A_2 \arrow[rr,] \arrow[dr, "\sim"'] && C_2 \arrow[dr, "\sim"] \\
    & B_2 \arrow[rr] && D_2 
    \end{tikzcd}
\]

The bottom square is a pullback since its opposite faces are equivalences, and
therefore the top face is also a pullback, so that the cube is a pullback in $\Ha^{\down}$.
\end{proof}

\begin{thm}
The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
$\Ha^{\downarrow}_{/\pi}$ exhibits $\Ha^{\downarrow}_{/_{\ulcorner} \pi}$ as a
subtopos.

As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
  $\Ha^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
  D}$ as a sheaf topos?}
\end{thm}
\begin{proof}
We prove this for the equivalent categories $\Ha^{\down}_{/\pi}$. This then
follows immediately from Proposition \ref{prop:lex.modalities.subtoposes} by
noting that the objects of $\Ha^{\down}_{/_{\ulcorner} \pi}$ are precisely those objects
in $\Ha^{\down}_{/\pi}$ whose terminal morphism is in $\term{cartesian}_{\pi}$.
\end{proof}

@@

\section{Appendix}
\begin{lem}\label{lem:slice.cone.equiv}
There is an equivalence $S^{\triangleleft} \simeq \Hom_{\Ha}(!_0, S)$ over
$\down$, natural in $S$.
\end{lem}
\begin{proof}
\jaz{TODO}
\end{proof}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}
\begin{proof}
\jaz{To Type}
\end{proof}

\begin{lem}\label{lem:kan.extending.cone.adds.initial}
If $\Ca$ is an $\infty$-category with an initial object, then the restriction
$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
initial object. 
\end{lem}
\begin{proof}
\jaz{TODO}
\end{proof}

\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
\end{lem}
\begin{proof}
For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that
\jaz{To Type}
\end{proof}

\begin{lem}\label{lem:every.type.weakly.contractible.colimit}
Every homotopy type $S$ is the colimit of the weakly contractible diagram
$S^{\triangleleft} \to \ast^{\triangleleft} \xto{!_0} \Ha$.
\end{lem}
\begin{proof}
We note that $!_0$ is the extension of the diagram $\ast : \ast \to \Ha$ by an
initial object. Therefore, by Lemma
\ref{lem:extending.diagram.with.initial.object.has.same.colimit}, this diagram
has the same colimit as $S \to \ast \xto{\ast} \Ha$. The colimit of this diagram
is $S$, because $\Ha$ is generated by the point $\ast$ --- see (cite). 
\end{proof}
